Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-10-01 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

In this study the following macroscopic loading condition was considered: 
\KB{add $\overline{\mathbf{F}}$ that you use in the analysis? this should be the most general case. How o you deal with the loading orientation $\theta$? }

 To determine the initial stiffness of the structures  we performed a linear elastic analysis. \KB{ Which one to calculate the stiffness? Explain how do you conduct the analysis with different loading orientations}

@@

\section{Optimization Analysis}
In an effort to identify lattice configurations resulting in large critical loads, we used  a Python
implementation of the Covariance Matrix Adaptation Evolution
Strategy (CMA-ES) \citep{hansen2003}.  CMA-ES is an evolutionary
algorithm that is used to solve optimization/inverse problems
by iteratively solving several forward problems to adjust
a covariance matrix of the solution. CMA-ES is a derivative
free algorithm, well suited for optimization problems of
high dimensionality.

\KB{this is not very clear. are we optimizing structures with circular or rectangular cross section? Which parameters do we keep fixed? Add a schematic}

@@

The parameters that need to be determined to achieve large critical loads are: the number of diagonals, the mass ratio ($\lambda$) of non-diagonals to diagonal, and the separation between each even set of diagonals. For this optimization problem, the number of optimization variables increases with the number of diagonal incorporated in the model. Thus, the total number of parameters are $1+(N-1) + (N \text{ mod } 2)/N$ for a given optimization instance with $N$ number of diagonals. An illustration for an optimization structure with $N=5$ is shown \cref{OptimizationSchematic}.

\begin{itemize}
\item the structure's mass ratio $\lambda$ (keeping the total structure volume constant, as well as distributing the mass evenly through all diagonal and non-diagonal elements respectively) and \item the separation of the even numbered diagonal elements from the non-diagonal junction. Separate instances of the optimization algorithm are analyzed for different numbers of diagonal reinforcements. For simulations with odd number of diagonal reinforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry. 
\end{itemize}

>>>>

In this study the following uniaxial macroscopic loading condition was considered: \begin{equation}
\overline{\mathbf{F}} = \begin{bmatrix}
0&0\\
0&-1
\end{bmatrix} 
\end{equation}

In order to investigate the structure's buckling and elastic stiffness response in all directions, we rotate the unit cell model by angle $\theta$ and re-apply the above periodic boundary conditions using the rotated geometry coordinates. This approach allows us to rotate the base orthogonal coordinate system with respect to the unit cell.

To determine the initial stiffness of the structures we performed a linear elastic analysis. To calculate stiffness we use a displacement controlled simulation and extract the total reaction force from the model. To obtain the structures response to varying angle, we follow the simple procedure detailed in the previous paragraph to rotate the boundary condition. Knowing the displacement applied and the total reaction force, we can use this information to compute the structural stiffness.

@@

\section{Optimization Analysis}
In an effort to identify lattice configurations resulting in large critical loads, we used a Python implementation of the Covariance Matrix Adaptation Evolution Strategy (CMA-ES) \citep{hansen2003}. CMA-ES is an evolutionary
algorithm that is used to solve optimization/inverse problems by iteratively solving several forward problems to adjust a covariance matrix of the solution. CMA-ES is a derivative free algorithm, well suited for optimization problems of high dimensionality and non-linear parameter topology.

@@

The parameters that need to be determined to achieve large critical loads are: the number of diagonals, the mass ratio ($\lambda$) of non-diagonal to diagonal members, and the separation between each even set of diagonals. For this optimization problem, the number of optimization variables increases with the number of diagonals incorporated in the model. Thus, the total number of parameters are $1+(N-1) + (N \text{ mod } 2)/N$ for a given optimization instance with $N$ number of diagonals. An illustration for an optimization structure with $N=5$ is shown \cref{OptimizationSchematic}. Note, for simulations with odd number of diagonal reinforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry.
